\documentclass[../main]{subfiles}
\begin{document}

\chapter*{Preface to Second Edition}
\addcontentsline{toc}{chapter}{Preface to Second Edition}

Nine years have passed since the publication of this book, during which time it has been awarded the warm reception of students of algebra and algebraic geometry in the United States, in Europe, as well as in Japan.

In this revised and enlarged edition, I have limited alternations on the original text to the minimum. Only Ch. 6 has been completely rewritten, and the other chapters have been left relatively untouched, with the exception of pages
37, 38, 160, 176, 216, 252, 258, 259, 260.

On the other hand, I have added an Appendix consisting of several sections, which are almost independent of each other. Its purpose is twofold: one is to prove the theorems which were used but not proved in the text, namely Eakin’s theorem, Cohen’s existence theorem of coefficient rings for complete local rings of unequal characteristic, and Nagata’s Jacobian criterion for formal power series rings. The other is to record some of the recent achievements in the area connected with PART II. They include Faltings’ simple proof of formal smoothness of the geometrically regular local rings, Marot’s theorem on Nagata rings, my theory on excellence of rings with enough derivations in characteristic 0, and Kunz’ theorems on regularity and excellence of rings of characteristic $p$.

I should like to record my gratitude to my former students M. Mizutani and M. Nomura, who read this book carefully and proved Th.\ref{thm:101} and Th.\ref{thm:099}.


\end{document}